Procedural generation of levels fot he angry birds videogame using evolutionary computation\\

### 2019-05-13 IEEE_ConferenceOnGames/article_english.tex
Update 13/5/2019 13:57

\begin{itemize}
    \item Total requiered levels
    \item Restrictions to pieces or piece-material combinations that cannot be placed or used in the levels, in this case if the file specifies that a \textit{CIRCLE} made out of \textit{ICE} cannotplaced the system must be able to verify that said combination is not used.
    \item Total number of pigs, this value can be a single value or a range of values that represent how many pigs must be placed on a level.
    \item The amount of time in which the system must give an output.
\end{itemize}

@@

>>>>

\begin{itemize}
    \item Total required levels
    \item Restrictions to pieces or piece-material combinations that cannot be placed or used in the levels, in this case if the file specifies that a \textit{CIRCLE} made out of \textit{ICE} cannotplaced the system must be able to verify that said combination is not used.
    \item Total number of pigs, this value can be a single value or a range of values that represent how many pigs must be placed on a level.
    \item The amount of time in which the system must give an output.
\end{itemize}

@@

Since this group of mutations further ensures diversity in the populations a different way to evaluate the individuals is needed, by using the previous proposed method as a base a way to evaluate the \textit{"diversity"} and \textit{"uniqueness"} of a individual, for this we first remove the \textit{x} and \textit{y} position as well as the \textit{angle} errors in order to add two new evaluation formulas as follows:

\begin{itemize}
    \item Hamming distance: a simle explanation for the \textit{Hamming distance} is that it is a calculation applied to a pair of strings where the obecive is to find the minimum required number of substitutions required in order to convert a string exactly the same as the other, its formula is shown in equation \ref{hamming_distance}, since the formula itself locates the minimum required number of substitutions then we compare the individual with the rest of the population trying to found the maximum number of substitutions required efectively using the formula to give a better fitness to those individuals that are different from the group.
    \item Shannon entropy: the shannon entropy is used on information theory to calculate the disorder or uncertainty, in this case it will be used to determine if a level is \textit{"boring"} or \textit{"interesting"} based on the amount of entropy calculated according to the pieces used in a level where a low entropy is boring because if a determined level as a lot of repeated pieces then it will look simple, the formula used is shown in equation \ref{shannon_entropy} where the elements calculated are the pieces of a level and their appearance probability against all others.
\end{itemize}

\begin{equation}
    \begin{aligned}
    d = min \left\{ \ d(x,y): x,y \in C, if \: x \neq y, 1 \: else \: 0 \: \right\} \
    \end{aligned}
    \label{hamming_distance}
\end{equation}

\begin{equation}
    \begin{aligned}
    S = - \Sigma_i P_i \log P_i
    \end{aligned}
    \label{shannon_entropy}
\end{equation}
